%-------------------------
% Resume in Latex
% Author : Vidushi Wahal
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.575in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1 }{\small #2} & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}                                                                                                                               
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\Large EL HARROUGUI Mohamed}}
&    \textbf{{\Large Software R\&D Engineer}} \\
    %& 25 years old, Married, Moroccan.\\
&    \href{https://www.linkedin.com/in/el-harrougui/?locale=en_US}{www.linkedin.com/in/el-harrougui/?locale=en\_US}\\
& Mobile : +212-625-70-25-61 - Email : \href{mailto:elharrougui0@gmail.com}{elharrougui0@gmail.com}\\
& Address : Residence Marie Rose, Buildig 41, Apt 11, Sala Al-Jadida\\
\end{tabular*}
%\href{https://www.linkedin.com/in/el-harrougui/?locale=en_US}{www.linkedin.com/in/el-harrougui/?locale=en\_US}\\
%Mobile : +212-625-70-25-61 - Email : \href{mailto:elharrougui0@gmail.com}{elharrougui0@gmail.com}\\
%Address : 20200, Appt4, Imm69, Alworoud St, Beaus\'{e}jour, Casablanca\\

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Engineering Degree in Computer sciences and integration of IT systems}{}{}
{Hassan II University, Faculty of Sciences and Technologies, Mohammedia.}{Sep. 2015 -- Jul. 2018}
\resumeSubheading
{Bachelor of Mathematical and Computer Sciences}{}{}
{Mohammed V University, Faculty of Sciences, Rabat.}{Sep. 2012 -- Jul. 2015}
\resumeSubheading
{Baccalaur\'{e}at of Mathematical Sciences}{}{}
{El-khawarizmi High School, Beni mellal.}{Sep. 2011 -- Jul. 2012}
\resumeSubHeadingListEnd
%--------------------------------------

%-----------EXPERIENCE-----------------
\section{Experiences \& Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Taillis Labs}{Software R\&D Engineer / Full-Stack developer}{Casablanca, Morocco}
{Works on several projects: CRM, Healthcare, Digital identities... }{Jan. 2019 - Present}
\resumeItemListStart
\resumeItem{}{Participate in continuous sprint cycles of development, integration \& delivery.}
\resumeItem{}{Collaborate with extern team for design and development direction.}
\resumeItem{}{Analysis and troubleshooting of incidents and anomalies reported by testers or end-users.}
\resumeItem{}{End-user technical support and onboarding of new coming developers.}
\resumeItem{}{Publish articles on the patterns and the solutions used \& developed internally.}
\resumeItem{Front-End / Mobile:}{ReactJS / React-Native, Apollo-client, Prop-types, Styled-components... }
\resumeItem{Javascript tools:}{Lodash, Eslint, Babel, Webpack, Joi, Casl, MomentJS...}
\resumeItem{Back-end:}{NodeJS/ExpressJS, Jest, Graphql/Apollo-server, Axios, Microservices patterns, CQRS/Event sourcing, Kafka/Zookeeper, TypeORM, DB-migrate, PostgreSQL.}
\resumeItem{Third-party APIs integrations:}{MailGun, SendinBlue, Twilio, Hubspot, Messenger.}
\resumeItem{Agility \& CI/CD:}{Scrum/TDD, Jira, Git/GitLab, Docker/Docker-compose, Linux/ssh.}
\resumeItemListEnd

\resumeSubheading
{Taillis Labs}{Software R\&D Engineer / Front-end developer}{Casablanca, Morocco}
{Subscription cards management system}{Sep. 2018 - Dec. 2019}
\resumeItemListStart
\resumeItem{}{Performed software development tasks based on design specifications.}
\resumeItem{}{Collaborate with remote Indian back-end team in Scrum mode to deliver new features each two weeks.}
\resumeItem{Front-end:}{React, Redux/Redux Saga, Axios, Bootstrap, Git/GitLab... }
\resumeItemListEnd

\resumeSubheading
{110.55. Consulting}{Intern - Full-Stack Developer \& Jr. BI Consultant}{Casablanca, Morocco}
{CRM module of an educational marketplace management ecosystem}{Feb. 2018 - Aug. 2019}
\resumeItemListStart

\resumeItem{Front-end:}{Angular4, Bootstrap.}
\resumeItem{Back-end:}{Java7/JEE, Spring, PostgreSQL/Postgrest, Third-party APIs integrations (OneSignal, SMS).}
\resumeItem{BI Dev:}{Piloting of the CRM module, List of KPIs, Design of the system, Develop with Pentaho suite.}
\resumeItem{Methodology \& Design:}{Scrum/Asana, Git/Bitbucket, UML.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%--------------------------------------

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{\textbf{Languages}{: Javascript(ES6), HTML/CSS, Bootstrap, Java, Shell, PL/SQL, C/C++/Arduino.}}\vspace{-4pt}
\item{\textbf{Frameworks/Librairies}{: ReactJs, Redux, Jest, NodeJs/ExpressJs, JavaEE/Spring, Angular, Symfony3.}}\vspace{-6pt}
\item{\textbf{Design}{: Solid Principles, Patterns, Microservices/Monolithic architectures, Restful/Graphql APIs, UML, Merise.}}\vspace{-6pt}
\item{\textbf{Databases}{: PostgreSQL, MySQL, MongoDB. }}\vspace{-6pt}
\item{\textbf{CI/CD}{: Git/GitHub/GitLab/Bitbucket, Docker, Kafka, Linux, SSH.}}\vspace{-6pt}
\resumeSubHeadingListEnd

%--------Interests------------
\section{Extracurricular Activities}
\resumeSubHeadingListStart
\item{\textbf{Teaching \& Sharing Knowledge}{: Mathematics, Programming, Robotics. }}\vspace{-4pt}
\item{\textbf{Make smart robotic systems}{: Arduino, Rasberry, Competitions.}}\vspace{-4pt}
\item{\textbf{Technical blogging}{: LinkedIn, Medium.}}\vspace{-4pt}
\resumeSubHeadingListEnd



\end{document}
