\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.575in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1 }{\small #2} & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}                                                                                                                               
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\Large EL HARROUGUI Mohamed}}
&    \textbf{{\Large Software R\&D Engineer}} \\
    %& 25 years old, Married, Moroccan.\\
&    \href{https://www.linkedin.com/in/el-harrougui/?locale=en_US}{www.linkedin.com/in/el-harrougui/?locale=en\_US}\\
& Mobile : +212-625-70-25-61 - Email : \href{mailto:elharrougui0@gmail.com}{elharrougui0@gmail.com}\\%& Address : Residence Marie Rose, Buildig 41, Apt 11, Sala Al-Jadida\\
\end{tabular*}
%\href{https://www.linkedin.com/in/el-harrougui/?locale=en_US}{www.linkedin.com/in/el-harrougui/?locale=en\_US}\\
%Mobile : +212-625-70-25-61 - Email : \href{mailto:elharrougui0@gmail.com}{elharrougui0@gmail.com}\\
%Address : 20200, Appt4, Imm69, Alworoud St, Beaus\'{e}jour, Casablanca\\

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Engineering Degree in Computer sciences and integration of IT systems}{}{}
{Hassan II University, Faculty of Sciences and Technologies, Mohammedia.}{Sep. 2015 -- Jul. 2018}
\resumeSubheading
{Bachelor of Mathematical and Computer Sciences}{}{}
{Mohammed V University, Faculty of Sciences, Rabat.}{Sep. 2012 -- Jul. 2015}
\resumeSubHeadingListEnd
%--------------------------------------

%-----------EXPERIENCE-----------------
\section{Experiences \& Projects}
\resumeSubHeadingListStart

\resumeSubheading
{ATOS on Behalf of Le Groupe La Poste, France}{Software R\&D Engineer}{Remote}
{Working on a set of services intended to provide various address data from postal repositories.}{Dec. 2020 - Present}
\resumeItemListStart

\resumeItem{}{Develop new functionalities and work on improving and automating CI / CD pipelines.}
\resumeItem{}{Work on the optimization of the treatments made by the application.}
\resumeItem{}{Ensure high availability and maintenance of the application and its technical and functional update.}
\resumeItem{}{Ensure clear and up-to-date documentation of the various technical aspects of the application.}
\resumeItem{}{Synchronize with the several multicultural stakeholders interfering on the project.}
\resumeItem{}{Participate in the agility ceremonies and in the improvement of software development practices.}
\resumeItem{Développement:}{Java, JUnit, Spring, Gitlab, ElasticSearch, MySQL, Talend, Bash, Javascript... }
\resumeItem{CI/CD:}{Jenkins, Docker, Openshift, IAAS...}
\resumeItem{Monitoring:}{Kibana, Grafana, Logstach, Prometheus...}
\resumeItemListEnd

\resumeSubheading
{Taillis Labs}{Software R\&D Engineer / Full-Stack developer}{Casablanca, Morocco}
{Works on several projects: CRM, Healthcare, Digital identities... }{Sep. 2018 - Nov. 2020}
\resumeItemListStart
\resumeItem{}{Participate in continuous sprint cycles of development \& integration \& delivery.}
\resumeItem{}{Collaborate with external-remote-multicultural teams for applications design and development.}
\resumeItem{}{Analysis and troubleshooting of incidents and anomalies reported by testers or end-users.}
\resumeItem{}{End-user technical support and on-boarding of new coming developers.}
\resumeItem{}{Publish articles on the patterns and the solutions used \& developed internally.}
\resumeItem{Front-End / Mobile:}{ReactJS / React-Native, Redux/Redux Saga, Axios, Apollo-client, Styling...}
\resumeItem{Back-end:}{ExpressJS, Jest, Apollo-server, CQRS/Event sourcing, Kafka, TypeORM, PostgreSQL.}
\resumeItem{Third-party APIs integrations:}{MailGun, SendinBlue, Twilio, Hubspot, Messenger.}
\resumeItem{Agility \& CI/CD:}{Scrum/TDD, Jira, Git/GitLab, Docker/Docker-compose, Linux/ssh.}
\resumeItemListEnd

\resumeSubheading
{110.55. Consulting}{Intern - Full-Stack Developer \& Jr. BI Consultant}{Casablanca, Morocco}
{CRM module of an educational marketplace management ecosystem}{Feb. 2018 - Aug. 2019}
\resumeItemListStart

\resumeItem{Front-end:}{Angular4, Bootstrap.}
\resumeItem{Back-end:}{Java7/JEE, Spring, PostgreSQL/Postgrest, Third-party APIs integrations (OneSignal, SMS).}
\resumeItem{BI Dev:}{Piloting of the CRM module, List of KPIs, Design of the system, Develop with Pentaho suite.}
\resumeItem{Methodology \& Design:}{Scrum/Asana, Git/Bitbucket, UML.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%--------------------------------------

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{\textbf{Languages}{: Java, Javascript, Bash,  C/C++/Arduino, SQL, PL/SQL, JSON, YAML, XML/HTML, CSS.}}\vspace{-4pt}
\item{\textbf{Frameworks/Librairies}{: ReactJs, Redux, Jest, ExpressJs, JavaEE/Spring, JUnit, Angular, Symfony.}}\vspace{-6pt}
\item{\textbf{Design}{: Solid Principles, Patterns, Microservices/Monolithic architectures, Restful/Graphql APIs, UML, Merise.}}\vspace{-6pt}
\item{\textbf{Data}{: PostgreSQL, MySQL, MongoDB, ELK Stack, Kafka, Talend, Pentaho suite.}}\vspace{-6pt}
\item{\textbf{CI/CD}{: Git/GitHub/GitLab/Bitbucket, Docker, Jenkins, Openshift/Kubernetes, Scripting, SSH.}}\vspace{-6pt}
\resumeSubHeadingListEnd

%--------Interests------------
\section{Extracurricular Activities}
\resumeSubHeadingListStart
\item{\textbf{Teaching \& Sharing Knowledge}{: Mathematics, Programming, Robotics. }}\vspace{-4pt}
\item{\textbf{Make smart robotic systems}{: Arduino, Rasberry, Competitions.}}\vspace{-4pt}
\item{\textbf{Technical blogging}{: LinkedIn, Medium.}}\vspace{-4pt}
\resumeSubHeadingListEnd



\end{document}
